Reanalysis Step 5: Outcome Analysis with Full Four-Treatment Interaction (Monotherapy Only)

### 2025-09-02 reanalysis-5-outcome_analysis-full_interaction.qmd
monotherapy ix

---
title: "Reanalysis Step 5: Outcome Analysis with Full Four-Treatment Interaction"
subtitle: "IPTW-weighted analysis of lapse × DR severity × 4-level treatment interactions"
author: "Erik Westlund"
date: "`r Sys.Date()`"
format: html
---

@@

@@

# Create consistent analysis variables across all imputed datasets
for (i in 1:n_imputations) {
  imputed_datasets[[i]] <- imputed_datasets[[i]] |>
    mutate(
      # First, check treatment overlaps for diagnostic purposes
      n_treatments = other_inject + anti_VEGF + focal_laser_flag + PRP_flag,

@@

      # Ensure lapse is properly coded
      ever_lapse_binary = factor(ever_lapse_binary, levels = c(0, 1),
                                 labels = c("No_Lapse", "Lapsed"))
    )
}

>>>>

---
title: "Reanalysis Step 5: Outcome Analysis with Full Four-Treatment Interaction (Monotherapy Only)"
subtitle: "IPTW-weighted analysis of lapse × DR severity × 4-level treatment interactions - Restricted to monotherapy patients"
author: "Erik Westlund"
date: "`r Sys.Date()`"
format: html
---

@@

**Note:** This analysis is restricted to monotherapy patients only (n_treatments ≤ 1) to avoid complexity from overlapping treatments.

@@

# Create consistent analysis variables across all imputed datasets
for (i in 1:n_imputations) {
  imputed_datasets[[i]] <- imputed_datasets[[i]] |>
    mutate(
      # First, check treatment overlaps for diagnostic purposes
      n_treatments = as.numeric(as.character(other_inject)) + 
                     as.numeric(as.character(anti_VEGF)) + 
                     as.numeric(as.character(focal_laser_flag)) + 
                     as.numeric(as.character(PRP_flag)),

@@

      # Ensure lapse is properly coded
      ever_lapse_binary = factor(ever_lapse_binary, levels = c(0, 1),
                                 labels = c("No_Lapse", "Lapsed"))
    ) |>
    # RESTRICT TO MONOTHERAPY PATIENTS (n_treatments == 0 or 1)
    filter(n_treatments <= 1)

  log_message(paste0("Imputation ", i, ": ", nrow(imputed_datasets[[i]]), 
                     " patients after restricting to monotherapy"))
}
